\documentclass[a4paper,12pt]{article}
\usepackage{tabularx}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\rhead{\today}
\lhead{Project Plan - M2theM}
\rfoot{Page \thepage}

\title{\textbf{Agile Project Plan Document}}
\author{}
\date{}


\begin{document}

\thispagestyle{empty}
\renewcommand{\arraystretch}{2}

\maketitle

\begin{tabularx}{\textwidth}{|l|X|}
	\hline
		\textbf{{\huge Project:}} &
		\textbf{{\huge Movie Madness}}\\
	\hline
		Release: &
		1.0\\
	\hline
		Date: &
		\today \\
	\hline
		&
		\\
	\hline
		{\Large Author:} &
		{\Large Method to the Madness}\\
	\hline
		Owner: &
		DevAcademy\\
	\hline
		Client: &
		Deloitte\\
	\hline
		Version No.: &
		1.0\\
	\hline
	
\end{tabularx}

\newpage

\tableofcontents

\newpage

\section{Project Plan}

\subsection{Purpose}

For the initial release of our project we will create a website that will be used to display the sample data within the read-only database provided, the website must have at least one dynamic page, allowing the data displayed to change depending on what the user requested. To do this we shall use a RESTful API implemented through Spring Boot and Thymeleaf to handle our back-end and the connection between server and client.

\subsection{Plan Description}

There are two halves of the initial project to be worked upon. In the back-end, the database must be accessed, sorted, and served to the front-end. The front-end must receive and display this data, as well as provide the back-end with the user's input with which to sort the data.

\subsection{Prerequisites}

The prerequisites required to begin this project are as follows:

- A private GitHub repository in the Gateshead College organisation, where the project will be kept.

- A read-only database containing all necessary data (movies, reviews etc).

- Access to technologies taught during the DevAcademy course (allowing us to complete the project with resources that we have been taught).

\subsection{Project Plan}

\subsubsection{Quality Plan}

\subsubsection{Risk Plan}

\subsubsection{Acceptance Plan}

The product must deliver all data provided (in the given database) to a dynamic web page through which the user can manipulate how the data is displayed.

\end{document}
